Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-04-14 analysis/paper/paper.Rmd
Figure formatting
- Move figures to end of manuscript

- Format legend to have two rows

- Generate eps files at 84mm x 84 mm and save in "./analysis/paper/figures"

```{r Setup..., message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(fig.pos = "p")
knitr::opts_chunk$set(out.width = "100%", dpi = 300)
knitr::opts_chunk$set(eval = TRUE)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)

@@

```{r figure-1, fig.cap="Tiller sheath blight incidence progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years. Main plot irrigation treaments were permanently flooded (FLD) and alternate wetting and drying (AWD). Five different nitrogen treatments were applied depending on the experiment. In the 2015 experiment three nitrogen rate treatements were applied: no N (N0), 100 units of N (N100) and 180 units of N (N180). In the 2016 experiment, two nitrogen rate treatments were applied: 60 units of N (N60) and 180 units of N (N180)."}

ggplot(RAW_data,
       aes(x = ASMT,
           y = TShB_incidence,
           linetype = NRTE,
           shape = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = TRT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = TRT)) +
  scale_y_continuous(labels = function(x) paste0(x*100), limits = c(0, 1)) +
  scale_shape_discrete(labels = c("N0", "N100", "N120", "N60", "N180")) +
  scale_linetype_discrete(labels = c("N0", "N100", "N120", "N60", "N180")) +
  ylab("Tiller Sheath Blight Incidence (%)") +
  xlab("Assessment") +
  facet_grid(WMGT ~ YEAR) +
  labs(linetype = "Nitrogen treatment",
       shape = "Nitrogen treatment") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  theme(legend.position = "bottom")
```

@@

```{r figure-2, fig.cap="Tiller sheath blight severity progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years. Main plot irrigation treaments were permanently flooded (FLD) and alternate wetting and drying (AWD). Five different nitrogen treatments were applied depending on the experiment. In the 2015 experiment three nitrogen rate treatements were applied: no N (N0), 100 units of N (N100) and 180 units of N (N180). In the 2016 experiment, two nitrogen rate treatments were applied: 60 units of N (N60) and 180 units of N (N180)."}

ggplot(RAW_data,
       aes(x = ASMT,
           y = PERC_TIL_ShB,
           linetype = NRTE,
           shape = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = TRT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = TRT)) +
  scale_shape_discrete(labels = c("N0", "N100", "N120", "N60", "N180")) +
  scale_linetype_discrete(labels = c("N0", "N100", "N120", "N60", "N180")) +
  ylab("Tiller Sheath Blight Severity (%)") +
  xlab("Assessment") +
  facet_grid(WMGT ~ YEAR) +
  labs(linetype = "Nitrogen treatment",
       shape = "Nitrogen treatment") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  theme(legend.position = "bottom")
```

@@

```{r figure-3, fig.cap="Leaf sheath blight severity progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season in both years. Main plot irrigation treaments were permanently flooded (FLD) and alternate wetting and drying (AWD). Five different nitrogen treatments were applied depending on the experiment. In the 2015 experiment three nitrogen rate treatements were applied: no N (N0), 100 units of N (N100) and 180 units of N (N180). In the 2016 experiment, two nitrogen rate treatments were applied: 60 units of N (N60) and 180 units of N (N180)."}

ggplot(RAW_data,
       aes(x = ASMT,
           y = PERC_LEAF_ShB,
           linetype = NRTE,
           shape = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = TRT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = TRT)) +
  scale_shape_discrete(labels = c("N0", "N100", "N120", "N60", "N180")) +
  scale_linetype_discrete(labels = c("N0", "N100", "N120", "N60", "N180")) +
  ylab("Leaf Sheath Blight Severity (%)") +
  xlab("Assessment") +
  facet_grid(WMGT ~ YEAR) +
  labs(linetype = "Nitrogen treatment",
       shape = "Nitrogen treatment") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  theme(legend.position = "bottom")
```

@@

>>>>

```{r Setup..., message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(fig.pos = "p")
knitr::opts_chunk$set(out.width = "100%", dpi = 300)
knitr::opts_chunk$set(fig.width = 3.31)
knitr::opts_chunk$set(fig.height = 3.31)
knitr::opts_chunk$set(eval = TRUE)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)

@@

@@

@@

@@

# Figures {-}

```{r figure-1, fig.cap="Tiller sheath blight incidence progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years. Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD). Five different nitrogen treatments were applied depending on the experiment. In the 2015 experiment three nitrogen rate treatements were applied: no N (N0), 100 units of N (N100) and 180 units of N (N180). In the 2016 experiment, two nitrogen rate treatments were applied: 60 units of N (N60) and 180 units of N (N180)."}

ggplot(RAW_data,
       aes(x = ASMT,
           y = TShB_incidence,
           linetype = NRTE,
           shape = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = TRT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = TRT)) +
  scale_y_continuous(labels = function(x) paste0(x*100), limits = c(0, 1)) +
  scale_shape_discrete(labels = c("N0", "N100", "N120", "N60", "N180")) +
  scale_linetype_discrete(labels = c("N0", "N100", "N120", "N60", "N180")) +
  ylab("Tiller Sheath Blight Incidence (%)") +
  xlab("Assessment") +
  facet_grid(WMGT ~ YEAR) +
  labs(linetype = "N Treatment",
       shape = "N Treatment") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  theme(legend.position = "bottom") +
  guides(linetype = guide_legend(nrow = 2),
         shape = guide_legend(nrow = 2))

ggsave("./Figures/Sparks_Figure_1.eps", width = 84, height = 84, units = "mm")

```

```{r figure-2, fig.cap="Tiller sheath blight severity progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years. Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD). Five different nitrogen treatments were applied depending on the experiment. In the 2015 experiment three nitrogen rate treatements were applied: no N (N0), 100 units of N (N100) and 180 units of N (N180). In the 2016 experiment, two nitrogen rate treatments were applied: 60 units of N (N60) and 180 units of N (N180)."}

ggplot(RAW_data,
       aes(x = ASMT,
           y = PERC_TIL_ShB,
           linetype = NRTE,
           shape = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = TRT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = TRT)) +
  scale_shape_discrete(labels = c("N0", "N100", "N120", "N60", "N180")) +
  scale_linetype_discrete(labels = c("N0", "N100", "N120", "N60", "N180")) +
  ylab("Tiller Sheath Blight Severity (%)") +
  xlab("Assessment") +
  facet_grid(WMGT ~ YEAR) +
  labs(linetype = "N Treatment",
       shape = "N Treatment") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  theme(legend.position = "bottom") +
  guides(linetype = guide_legend(nrow = 2),
         shape = guide_legend(nrow = 2))

ggsave("./Figures/Sparks_Figure_2.eps", width = 84, height = 84, units = "mm")
```

```{r figure-3, fig.cap="Leaf sheath blight severity progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season in both years. Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD). Five different nitrogen treatments were applied depending on the experiment. In the 2015 experiment three nitrogen rate treatements were applied: no N (N0), 100 units of N (N100) and 180 units of N (N180). In the 2016 experiment, two nitrogen rate treatments were applied: 60 units of N (N60) and 180 units of N (N180)."}

ggplot(RAW_data,
       aes(x = ASMT,
           y = PERC_LEAF_ShB,
           linetype = NRTE,
           shape = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = TRT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = TRT)) +
  scale_shape_discrete(labels = c("N0", "N100", "N120", "N60", "N180")) +
  scale_linetype_discrete(labels = c("N0", "N100", "N120", "N60", "N180")) +
  ylab("Leaf Sheath Blight Severity (%)") +
  xlab("Assessment") +
  facet_grid(WMGT ~ YEAR) +
  labs(linetype = "N Treatment",
       shape = "N Treatment") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  theme(legend.position = "bottom") +
  guides(linetype = guide_legend(nrow = 2),
         shape = guide_legend(nrow = 2))

ggsave("./Figures/Sparks_Figure_3.eps", width = 84, height = 84, units = "mm")
```
